\chapter{Chapter on ABC}
The content of the body depends on the purpose of the report, and whether it is a report of primary or secondary research.

A report of primary research (based on your own observations and experiments) would include:
\begin{enumerate}
\item
Literature review (what other people have written about this topic. See here for some hints on writing a literature review. The literature review should lead towards your research question.
\item
Method (summarises what you did and why). Use the past tense.
\item
Findings or results (describes what you discovered, observed, etc in your observations and experiments). Use the past tense.
\item
Discussion (discusses and explains your findings and relates them to previous research). Use the present tense to make generalisations.
\end{enumerate}
A report of secondary research (based on reading only) would include:
\begin{enumerate}
\item
Information organised under appropriate topics with sub-headings. It is unlikely that your report will discuss each source separately. You need to synthesise material from different sources under topic headings.
\item
Analysis/discussion of the sources you are reporting.
\end{enumerate}
\section{How to use citations}
Using parencite: \parencite{RN4}.

Using cite: \cite[prenote][postnote]{RN4}.

Using textcite: \textcite{RN4}.

Using footcite: \footcite[prenote][postnote]{RN4}.

Using smartcite: \smartcite{RN4}.
 
Using cite*: \cite*{RN4}.

Using parencite*: \parencite*{RN4}.

Multiple references: \parencites[35]{RN4}[88--120]{RN6}[23]{RN3} % can be combined with the other cite styles

Using autocite: \autocite[prenote][postnote]{RN4}

Using citeyear: \citeyear{RN4}

Using citedate: \citedate{RN4}

Using citeauthor: \citeauthor{RN4}
 
Using citetitle: \citetitle{RN4}

Using parentext: \parentext{RN4}

Using brackettext: \brackettext{RN4}

\section{Second section}
\section{Third section}